\papertitle

### 2021-03-08 source_separation/paper/paper.tex
Add future work; add ref to SOL and orchestra used

		The orchestrations performed were static orchestrations, meaning a single onset of notes is created for each target, no matter if the target itself has multiple onsets.

@@

	\section{Future Work}\label{sec:futurework}
	Implementing these methods in Orchidea. We could improve the supervised methods by training them ourselves with data that fits our problem better. Adding a joint optimization to determine which instruments should be used in which sources.

>>>>

		The orchestrations performed were static orchestrations, meaning a single onset of notes is created for each target, no matter if the target itself has multiple onsets. The OrchideaSOL database of orchestral samples was used with Orchidea to create the orchestrations~\cite{Cella2020c}. This database contains recordings of extended playing techniques, which better fits the often noisy or inharmonic nature of the targets we used. The full orchestra, of which non-overlapping subsets were selected to orchestrate the subtargets, contained the following instruments: 8 violins, 4 violas, 3 cellos, 1 bass, 2 oboes, 2 flutes, 2 clarinets in B$\flat$, 2 bassoons, 2 trumpets, 2 trombones, and 2 French horns.

@@

	\section{Future Work}\label{sec:futurework}

	As we stated in Section \ref{sec:conclusions}, we believe that one of the reasons the supervised methods did not perform as well is because of the data they were trained on. Therefore, a natural next step is to train these models ourselves with sounds that are more applicable to computer-assisted orchestration.

	Another aspect we would like to work on is the assignment of the orchestras. Currently, the subset of the orchestra that is assigned to each sub-target is randomly selected. However, it is possible that this random assignment could reduce the quality of the final orchestration. If, for example, one of the sub-targets contains mostly low pitch content, but the orchestra assigned to it contains mostly violins, violas, flutes, and oboes, the resulting orchestration will suffer. To solve this problem, a step could be added that jointly-optimizes the the orchestras assigned to each sub-target, ultimately choosing an assignment that leads to the best orchestration of each sub-target.

	Finally, one or multiple of the separation methods we tested should be implemented in Orchidea in order to improve the orchestrations Orchidea is capable of creating. NMF performed the best across the targets we tested on, and therefore makes sense to be added to Orchidea. However, it could also make sense to add one of the musical source spearation methods, such as OpenUnmix, to allow users to choose different methods based on the targets they are orchestrating.
